In response to unforeseen circumstances preventing the training of the intended model, an innovative solution has been implemented through the development of a simulator for vehicle cruise control. This alternative system employs Tesseract OCR (Optical Character Recognition) to convert speed data into numerical values. Subsequently, a PID (Proportional-Integral-Derivative) controller is utilized to determine the appropriate output action based on the disparity between the desired and actual speed. This output action is then translated into a corresponding key press, aligning with the desired speed adjustments.
\\
The seamless integration of Tesseract OCR and PID control not only ensures accurate speed interpretation but also facilitates a responsive and efficient control mechanism for the vehicle. Notably, the flexibility of the code allows for the straightforward incorporation of the originally intended model, preserving the adaptability of the system to future enhancements. This strategic approach not only addresses the challenges posed by unforeseen obstacles but also lays the groundwork for future iterations, maintaining the system's potential for continuous improvement and evolution.

\section{Final Result}
Presenting a comprehensive video demonstration, the efficacy of the cruise control feature in GTA-V is meticulously showcased. The video underscores the seamless integration of Tesseract OCR and PID control, illustrating the system's nuanced ability to dynamically interpret in-game speed data through Tesseract OCR and execute precise adjustments via the PID controller. Audiences are invited to observe the virtual vehicle responding adeptly to diverse in-game scenarios, maintaining the desired speed with precision. The provided hyperlink facilitates direct access to a visual representation of the project's success, offering a firsthand perspective on the sophisticated control mechanism within the dynamic virtual realm of GTA-V. This video presentation serves not only as a visual complement to the technical intricacies outlined in the report but also as an engaging narrative of the cruise control system's proficiency within the gaming environment. For an immersive demonstration, please follow the link: \url{https://drive.google.com/file/d/1qhb-lCffd7_i3RC6IqrqWnJGbAAelngn/view?usp=sharing}.

\section{Other Important Links}
\begin{itemize}
    \item Link for the GitHub Organization where all the code of this project is: \url{https://github.com/DRAN-Drive-Autonomous}.
    \item Drive Link for the Analytics part: \url{https://drive.google.com/drive/folders/1hKAnlzI5grYIPix5mnLZJZc28c-z5qWl?usp=sharing}.
\end{itemize}