\section{The Area of Work}
Autonomous Vehicle are cars and trucks that can understand and navigate the environment with little to no help from a human driver. While consumers cannot yet buy a car that fully drives itself (Level 4 or 5 automation)\cite{J3016_202104}, the technology is under development and improving quickly. The self-driving cars being worked on today have many different sensors and cameras to capture information about the world. So, a big challenge in the field of Computer Science and Engineering is to make a Artificial Intelligent network which takes the captured information and gives the best possible action a car should in that state of environment. My project aims to try to build a network capable of taking some of the actions and to able to drive a car efficiently.

\section{Problem Addressed}
An autonomous vehicle is made with the goal to make travel of an individual safer than non autonoumus ones. The environment being partially observable and undeterministic, an autonomous vehicle should be prepared to take action based on any outcome. So an artificial intelligent model which can take decision in any type of environment is desired. Thus we need a model that can learn and adapt on its own in any type of scenarios. This is why a neural network based model is ideal for the use case and forms the heart of any autonomous vehicle. Since driving a vehicle in not efficient, we need a simulator which can create a close-to real world environment. Grand Theft Auto - V fits this criteria perfectly. Thus the main objective is to design, train, and simulate a autonomous vehicle in GTA-V and try to make the model as efficient as possible.

\section{Existing System}
Currently, there are no legally operational and fully autonomous vehicles in the world. However, partially autonomous vehicles, such as cars and trucks with varying amounts of automation, from assistance for braking to aid changing lanes and parking, with some models even having a certain degree of automatic steering are running on the roads. Although it is still in its infancy, autonomous driving technology is becoming increasingly common and could radically transform our transport system.
\\
Currently there are several companies worldwide competing in the race of automation in aotomobiles like,
\begin{itemize}
    \item \textbf{Tesla} has been rolling out its autonomous cars with Level 2 automation for some past years and has also rolled out a beta-version of its software to upscale the level of autonomy in its vehicles.
    \item \textbf{Waymo} operates commercial self-driving taxi services in Phoenix, Arizona and San Francisco, CA. In October 2020, it was the only self-driving commercial service that operates without safety backup drivers in the vehicle at that time.
    \item \textbf{TuSimple} has developed a fleet of 50+ trucks and 18+ contracted customers in the last years, claiming that its tech can reduce transportation costs by 30\%. It is also backed by Nvidia and UPS, which is working with TuSimple to test its Level 4 autonomous trucks.
    \item \textbf{Zoox} is creating an entirely new autonomous vehicle targeted at the robo-taxi market. Zoox has applied the latest techniques in automotive, robotics and renewable energy to build a symmetrical, bi-directional battery-electric vehicle that solves for the unique challenges of autonomous mobility.
    \item \textbf{Aurora} recently announced it is working to apply its Aurora Driver platform (Level 4) to heavy-duty Class 8 trucks. 
\end{itemize}





