In this project, I discussed about many criterions used to design a autonomous vehicles, compared machine learning and deep learning for the task, discussed about cruise control and the mathematics involved behind it. This project involves developement of several programs, be it for data collection, preprocessing, analysing, augmentation, collecting data in a array. This gave insight about how difficult and crucial data collection is in making a Artificially Intelligent Model. Along with this, We discussed about different layers and their functionalities in Vision Transformer and a hands-on implementation of Vision Transformer is also done, though it could not be trained due to certain unseen circumstances. A hands-on implementation in developing a simple cruise control network for a vehicle was also done which gave us insights about how important system efficiency is in making a AI Network, as there was a gap of 0.5 seconds in each iteration in my system which greatly affected the performance. Finally, simulation of cruise control feature in GTA-V was done which helped in understanding the difference between theoretical and practical changes in running AI Models as their were several hyperparameter tuning which had to be done to make the car work as shown in video.

\section{Scope of Future Work}
Work that could be done in future:
\begin{itemize}
    \item Training the model or build another model to acheive desired accuracy.
    \item Make a network to easily visualize and also efficienty predict the vehicle action.
    \item Training time-series model and compare the models. 
\end{itemize}